### 2013-09-17 main.tex
add icra nyu paper
remove "will"
title page, smaller borders

\documentclass[12pt,toc=bibnumbered, a4paper,twoside,DIV=calc]{scrbook}

\usepackage{hyperref}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{calc}
\usepackage{refstyle}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{multicol}
%\usepackage{pslatex}
\usepackage{microtype}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{mdwlist}
\usepackage{url}
\usepackage[noend]{algpseudocode}
\usepackage[small]{caption}
\usepackage{setspace}
\usepackage{color}
\usepackage{minted}

@@

%\usepackage{garamondx}
%\usepackage[urw-garamond]{mathdesign}
\usepackage{xspace}
\onehalfspacing
\KOMAoptions{DIV=last}

@@

@@

\begin{spacing}{1}
\begin{titlepage}
\begin{center}
\vspace*{1in}
\textbf{{\LARGE On Learning Structured Prediction For Semantic Segmentation}}
\par
\vspace{1.5in} {\large Andreas Christian M\"uller}
\par \vspace{0.5in}
Abteilung VI, Autonomie Intelligente Systeme \par
Institut f\"ur Informatik
\par \vspace{0.5in}
Friedrich-Willhelm Universit\"at Bonn \par
\vspace{0.5in} September 2013 \end{center}

\end{titlepage}

@@

\chapter{Latent CRFs for Semantic Segmentation}\label{ch:latent}

>>>>

\documentclass[12pt,toc=bibnumbered, a4paper,twoside,DIV=11]{scrbook}
%\documentclass[12pt,toc=bibnumbered, a4paper,twoside]{book}

\usepackage{hyperref}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{calc}
\usepackage{refstyle}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{multicol}
%\usepackage{pslatex}
\usepackage{microtype}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{tabu}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{mdwlist}
\usepackage{url}
\usepackage[noend]{algpseudocode}
\usepackage[small]{caption}
\usepackage{setspace}
\usepackage{color}
\usepackage{minted}

@@

%\usepackage{garamondx}
%\usepackage[urw-garamond]{mathdesign}
\usepackage{xspace}
\onehalfspacing
%\KOMAoptions{DIV=last}

@@

\setlength{\tabcolsep}{2pt}

@@

\begin{spacing}{1.6}
\begin{titlepage}

\begin{center}
\Large\sffamily
\vspace*{1cm}
\textbf{{\huge Learning Structured Prediction For Semantic Image Segmentation}}\\[5mm]
Dissertation\\%[3mm]
zur\\%[3mm]
Erlangung des Doktorgrades (Dr.\ rer.\ nat.)\\%[3mm]
der\\%[3mm]
Mathematisch-Naturwissenschaftlichen Fakult\"at\\%[3mm]
der\\%[3mm]
Rheinischen Friedrich-Wilhelm Universit\"at Bonn\\%[3mm]
vorgelegt von\\%[5mm]
{\LARGE Andreas Christian M\"uller}\\%[5mm]
aus\\%[3mm]
Offenbach am Main\\%[10mm]
Bonn, September 2013
\end{center}
\end{titlepage}

@@

\include{nyu/paper}
